---
title: "Assignment_B1"
author: "Han Wang"
date: "2023-11-01"
output: github_document
Roxygen: list(markdown = TRUE)
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(datateachr) 
library(tidyverse)
```

## Exercise 1: Make a Function (25 points) & Exercise 2: Document the Function

In this exercise, you'll be making a function and fortifying it. The function need not be complicated. The function need not be “serious”, but shouldn't be nonsense.

In the same code chunk where you made your function, document the function using roxygen2 tags.

In my previous MDA, I analyzed the cancer_sample including grouping by diagnosis and then summarizing various statistics for columns like radius_mean and symmetry_mean. This is a repeated action and thus can be encapsulated in a function below.

```{R}
#' @title Summarize the statistics of a given variable grouped by another variable
#' @details This function computes summary statistics for a specified column grouped by another column.
#' @param data A dataframe containing the data
#' @param group_var The variable to group by (as a symbol)
#' @param stat_var The variable on which to compute the statistics (as a symbol)
#'
#' @return A dataframe with min, max, mean, median, standard deviation, and count for the specified variable, grouped by the given grouping variable.
summarize_stats <- function(data, group_var, stat_var){
  if (nrow(data) == 0) {
    return(data.frame())
  }
  data %>%
    group_by({{group_var}}) %>%
    summarise(
      min=min({{stat_var}}, na.rm = TRUE),
      max=max({{stat_var}}, na.rm = TRUE),
      mean=mean({{stat_var}}, na.rm = TRUE),
      median=median({{stat_var}}, na.rm = TRUE),
      sd=sd({{stat_var}}, na.rm = TRUE),
      n=n()
    )
}
```

## Exercise 3: Include examples

```{r}
# Example 1: Computing statistics for radius_mean grouped by diagnosis
# This example demonstrates how to use the function to compute the summary statistics
# for the `radius_mean` column, grouping the data by the `diagnosis` column. 
# The resulting dataframe will contain the minimum, maximum, average, median, 
# standard deviation and count of `radius_mean` values for each unique `diagnosis`.
summarized_radius_mean <- summarize_stats(cancer_sample, diagnosis, radius_mean)
print(summarized_radius_mean)
```
```{r}
# Example 2: Computing statistics for symmetry_mean grouped by diagnosis
# This example demonstrates the use of the function to compute 
# summary statistics for the `symmetry_mean` column, again grouping by `diagnosis`.
# The results will show the summarized statistics for `symmetry_mean` based on each 
# unique value in the `diagnosis` column.
summarized_symmetry_mean <- summarize_stats(cancer_sample, diagnosis, symmetry_mean)
print(summarized_symmetry_mean)
```

```{r}
# Example 3: Computing statistics for texture_mean grouped by diagnosis
# This example computes the summary statistics for the `texture_mean` column.
# The cancer_sample is grouped by `diagnosis` to see how the texture_mean values differ 
# across different diagnoses.
summarized_texture_mean <- summarize_stats(cancer_sample, diagnosis, texture_mean)
print(summarized_texture_mean)
```
```{r}
# Example 4: Computing statistics for compactness_mean grouped by diagnosis
# This example computes the summary statistics for the `compactness_mean` column,
# grouping the data by the `diagnosis` column. It allows us to analyze how the 
# compactness mean values are distributed based on the diagnosis of the cancer.
summarized_compactness_mean <- summarize_stats(cancer_sample, diagnosis, compactness_mean)
print(summarized_compactness_mean)
```
```{r}
# Example 5: Computing statistics for smoothness_mean grouped by diagnosis
# For the `smoothness_mean` column, it is grouped by `diagnosis`, giving 
# an insight into the distribution of smoothness mean values across different cancer diagnoses.
summarized_smoothness_mean <- summarize_stats(cancer_sample, diagnosis, smoothness_mean)
print(summarized_smoothness_mean)
```
## Exercise 4: Test the Function

### Setup 
```{r}
library(dplyr)
library(testthat)
```
### Generating a Testing Dataset
This dataset has 4 types of variables:
1. A grouping variable group with three levels: a, b, and c.
2. A numeric variable value with some NAs.
3. An integer variable value_int.
4. A character variable value_char.
```{r}
# Create a sample dataset
set.seed(123) # for reproducibility

test_data <- data.frame(
  group = sample(letters[1:3], 100, replace = TRUE),
  value = rnorm(100),
  value_int = sample(1:10, 100, replace = TRUE),
  value_char = sample(letters[4:6], 100, replace = TRUE)
)

# Introduce some NA's
test_data[sample(1:100, 10), "value"] <- NA
```

### Testing

```{r}
# Test the function
test_that("Test summarize_stats function", {

  # 1. Vector with no NA's
  result_1 <- summarize_stats(test_data, group, value_int)
  expect_true(!any(is.na(result_1$mean)))

  # 2. Vector that has NA's
  result_2 <- summarize_stats(test_data, group, value)
  expect_true(any(is.na(test_data$value)))
  expect_true(!any(is.na(result_2$mean)))

  # 3. Vector of a different type
  # Note: Summarizing a character vector will throw an error in this context.
  # So, we are expecting an error in this case.
  expect_error(summarize_stats(test_data, group, value_char))
  expect_error(summarize_stats(test_data, group, cur_date))

  # 4. Vector of length 0
  empty_data <- test_data[0, ]
  result_4 <- summarize_stats(empty_data, group, value)
  expect_equal(nrow(result_4), 0)
})
```